---
title: "Recruitment and Retention"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    css: custom.css
    social: menu
    logo: PAN_logo3.png
    favicon: PAN_logo3.png
runtime: shiny
editor_options: 
  chunk_output_type: console
---

```{=html}
<style type="text/css">

  .chart-title {  /* chart_title  */
    font-size: 22px;

</style>
```
<!-- Server -->

```{r setup, include=FALSE}

library(tidyverse)
library(shiny)
library(flexdashboard)
# devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0")
# Need to use the above to collapse rows properly
library(kableExtra)

# section to connect to Google Drive
library(googledrive)
# file with info for service account 
googledrive::drive_auth(path = "pan-mindcrowd-uploads-ddf6b0dbe662.json")

# Option to silence the messages coming from the Google Drive library
options(googledrive_quiet = TRUE)

```

```{r load data}

with_drive_quiet(
  drive_download(as_id("https://drive.google.com/file/d/1EzECr3ExclMk1S_HkwBrE10jGtkKKFcF"), 
                 overwrite = TRUE)
)
load("mindcrowd_screening_data.Rdata")

recruitment <- data

with_drive_quiet(
  drive_download(as_id("https://drive.google.com/file/d/1Dk4kou56uJIK71qhh4TCE1NDy7_nZLFS"), 
                 overwrite = TRUE)
)
load(paste0("mindcrowd_campaign_codes.Rdata"))

```



```{r descriptive tables}

# Overall recruitment
overall_table <- recruitment %>%
  select(area, race_group, age_group, task_group) %>%
  rbind(recruitment %>% 
          select(area, race_group, age_group, task_group) %>%
          mutate(area = "Total")) %>%
  group_by(area, race_group, age_group) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(age_group, race_group, area, fill = list(n = 0)) %>%
  pivot_wider(id_cols = c(race_group, age_group),
              names_from = area,
              values_from = n)  %>%
  select(Age = age_group, `Race/Ethnicity` = race_group,
         Atlanta, Baltimore,  Miami, Tucson, Total) %>%
  arrange(Age, `Race/Ethnicity`) %>%
  mutate(across(where(is.factor), as.character)) %>%
  rbind(., c("Total", "", colSums(.[-(1:2)]))) %>%
  as.data.frame() %>%
  kable() %>% 
  kable_styling(full_width = F) %>%
  # column_spec(7,border_left = T) %>%
  # row_spec(9, extra_css = "border-bottom: 1px solid") %>%
  collapse_rows(columns = 1:2, valign = "top") %>%
  scroll_box(width = "100%", height = "800px")

# Overall recruitment by sex
gender_table <- recruitment %>%
  select(area, age_group, sex) %>%
  rbind(recruitment %>% 
          select(area, age_group, sex) %>%
          mutate(sex = "Total")) %>%
  group_by(sex, age_group, area) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(age_group, area, sex, fill = list(n = 0)) %>%
  pivot_wider(id_cols = c(age_group, area),
              names_from = sex,
              values_from = n)  %>%
  select(Age = age_group, Area = area, 
         Male, Female, Total) %>%
  arrange(Age, Area) %>%
  mutate(across(where(is.factor), as.character)) %>%
  rbind(., c("Total", "", colSums(.[-(1:2)]))) %>%
  kable() %>% 
  kable_styling(full_width = F) %>%
  # column_spec(8,border_left = T) %>%
  # row_spec(18, extra_css = "border-bottom: 1px solid") %>%
  collapse_rows(columns = 1:2, valign = "top") %>%
  scroll_box(width = "100%", height = "800px")

# Split by area
city_table <- recruitment %>%
  select(area, race_group, age_group, task_group) %>%
  rbind(recruitment %>% 
          select(area, race_group, age_group, task_group) %>%
          mutate(area = "Total")) %>%
  group_by(area, race_group, age_group, task_group) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(age_group, race_group, task_group, area, fill = list(n = 0)) %>%
  pivot_wider(id_cols = c(race_group, age_group, task_group),
              names_from = area,
              values_from = n) %>%
  mutate(across(Atlanta:Tucson, ~ifelse(is.na(.), 0, .))) %>%
  select(Age = age_group, `Race/Ethnicity` = race_group,  Performance = task_group, 
         Atlanta, Baltimore,  Miami, Tucson, Total) %>%
  arrange(Age, `Race/Ethnicity`, `Performance`) %>%
  mutate(across(where(is.factor), as.character)) %>%
  rbind(., c("Total", "", "", colSums(.[-(1:3)]))) %>%
  kable() %>% 
  kable_styling(full_width = F) %>%
  # column_spec(8,border_left = T) %>%
  # row_spec(27, extra_css = "border-bottom: 1px solid") %>%
  collapse_rows(columns = 1:2, valign = "top") %>%
  scroll_box(width = "100%", height = "800px")

# Split by test quantile
test_table <- recruitment %>%
  select(area, race_group, age_group, task_group) %>%
  rbind(recruitment %>% 
          select(area, race_group, age_group, task_group) %>%
          mutate(task_group = "Total")) %>%
  group_by(area, race_group, age_group, task_group) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(age_group, race_group, task_group, area, fill = list(n = 0)) %>%
  mutate(task_group = factor(str_to_title(task_group),
                             levels = c("Q2", "Q3", "Q4", "Total"))) %>%
  pivot_wider(id_cols = c(race_group, age_group, area),
              names_from = task_group,
              values_from = n) %>%
  mutate(across(Q2:Total, ~ifelse(is.na(.), 0, .))) %>%
  arrange(area, age_group, race_group) %>%
  select(Location = area, Age = age_group, `Race/Ethnicity` = race_group,
         everything()) %>%
  mutate(across(where(is.factor), as.character)) %>%
  rbind(., c("Total", "", "", colSums(.[-(1:3)]))) %>%
  kable() %>% 
  kable_styling(full_width = F) %>%
  # column_spec(7,border_left = T) %>%
  # row_spec(36, extra_css = "border-bottom: 1px solid") %>%
  collapse_rows(columns = 1:2, valign = "top") %>%
  scroll_box(width = "100%", height = "800px")

```

```{r campaign code table}

campaign_data <- data %>% 
  filter(campaign_code != "" & !is.na(campaign_code)) %>%
  mutate(campaign_code = toupper(campaign_code))

campaign_table <- campaign_data %>%
  count(campaign_code, race_group, age_group, area) %>%
  complete(campaign_code, race_group, age_group, area, fill = list(n = 0))  %>%
  mutate(race_age = paste(race_group, age_group)) %>%
  select(-c(age_group, race_group)) %>%
  pivot_wider(id_cols = c(area,campaign_code),
              names_from = race_age,
              values_from = n) %>%
  mutate(across(-campaign_code, ~ifelse(is.na(.), 0, .))) %>%
  arrange(area,campaign_code) %>%
  mutate(Total = rowSums(across(where(is.numeric)))) %>%
  filter(Total != 0) %>%
  rbind(c("Total", "", colSums(select(., -c(area, campaign_code))))) %>%
  kable(col.names = c("Area", "Campaign Code",
                      rep(c("50-59", "60-69", "70-79"), 3),
                      "Total")) %>%
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1)%>%
  add_header_above(c(" " = 2, "Hispanic" = 3, "Non-Hispanic Black" = 3, "Non-Hispanic White"  = 3, " " = 1)) %>%
  scroll_box(width = "100%", height = "800px")
  


```

```{r number to select from each group, eval = FALSE}

equal_proportions <- 45/9

younger_hispanic <- equal_proportions
younger_black <- equal_proportions
younger_white <- equal_proportions

older_hispanic <- equal_proportions
older_black <- equal_proportions
older_white <- equal_proportions

oldest_hispanic <- equal_proportions
oldest_black <- equal_proportions
oldest_white <- equal_proportions

```

```{r randomly selected data and table, eval = FALSE}

selected_list <- tibble(race_group = c("Hispanic/Latino", "Non-Hispanic Black", "Non-Hispanic White"),
                           `50-59` = c(younger_hispanic, younger_black, younger_white),
                           `60-69` = c(older_hispanic, older_black, older_white),
                           `70-79` = c(oldest_hispanic, oldest_black, oldest_white)) %>%
  pivot_longer(cols = -race_group, names_to = "age_group") %>%
  transmute(group = paste0(race_group, " ", age_group), value)

selected_data <- recruitment %>%
  mutate(group = paste0(race_group, " ", age_group)) %>%
  # https://stackoverflow.com/questions/66476142/sample-from-a-data-frame-using-group-specific-sample-sizes
  left_join(selected_list, by = "group") %>%
  group_by(area, group) %>%
  mutate(samp = sample(n())) %>%
  filter(samp <= ceiling(value)) %>%
  ungroup() %>%
  select(-c(value, samp))

# Will need to split download by recruitment center:
output$downloadData <- downloadHandler(
    filename = function() {
      paste0("selected_data_", format(Sys.Date(), "%y%d%m"), ".csv")
    },
    content = function(file) {
      write.csv(selected_data, file)
    }
  )

output$downloadDataAtl <- downloadHandler(
    filename = function() {
      paste0("selected_data_atlanta_", format(Sys.Date(), "%y%d%m"), ".csv")
    },
    content = function(file) {
      write.csv(selected_data[selected_data$area == "Atlanta",], file)
    }
  )

output$downloadDataBlt <- downloadHandler(
    filename = function() {
      paste0("selected_data_baltimore_", format(Sys.Date(), "%y%d%m"), ".csv")
    },
    content = function(file) {
      write.csv(selected_data[selected_data$area == "Baltimore",], file)
    }
  )

output$downloadDataMia <- downloadHandler(
    filename = function() {
      paste0("selected_data_miami_", format(Sys.Date(), "%y%d%m"), ".csv")
    },
    content = function(file) {
      write.csv(selected_data[selected_data$area == "Miami",], file)
    }
  )

output$downloadDataTuc <- downloadHandler(
    filename = function() {
      paste0("selected_data_tucson_", format(Sys.Date(), "%y%d%m"), ".csv")
    },
    content = function(file) {
      write.csv(selected_data[selected_data$area == "Tucson",], file)
    }
  )

selected_table <- selected_data %>%
  group_by(area, race_group, age_group, group) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  complete(age_group, race_group, area, fill = list(n = 0)) %>%
  pivot_wider(id_cols = c(race_group, age_group, group),
              names_from = area,
              values_from = n) %>%
  select(Age = age_group, `Race/Ethnicity` = race_group,
         Atlanta, Baltimore,  Miami, Tucson, group) %>%
  arrange(Age, `Race/Ethnicity`) %>%
  mutate(across(where(is.factor), as.character),
         Total = Atlanta + Baltimore + Miami + Tucson) %>%
  left_join(selected_list, by = "group") %>%
  mutate(Total = paste0(Total, " /", value*4)) %>%
  select(-c(group, value)) %>%
  rbind(., c("Total", "", 
             paste0(colSums(.[-c(1:2, ncol(.))]), " /", sum(selected_list$value, na.rm = T)), 
             paste0(sum(.[-c(1:2, ncol(.))]), " /", sum(selected_list$value, na.rm = T) * 4)
             )) %>%
  kable() %>% 
  kable_styling(full_width = F) %>%
  collapse_rows(columns = 1:2, valign = "top") %>%
  scroll_box(width = "100%", height = "500px")

```

<!-- UI -->

# Overall Recruitment

<br>

## Row

#### 

```{r}

overall_table

```

# Counts by City {data-navmenu="Counts by"}

<br>

## Row

#### 

```{r}

city_table

```

# Counts by Sex {data-navmenu="Counts by"}

<br>

## Row

#### 

```{r}
gender_table
```

# Counts by Test Level {data-navmenu="Counts by"}

<br>

## Row

#### 

```{r}
test_table
```


# Campaign Codes


<br>

## Row

#### 

```{r}

campaign_table

```

<br>


Note: Haven't pulled recruitment data yet.

# Help

App information:

This app currently displays screening data of participants in the PAN study. All tables display the same data.

Data:

Last updated: `r format(Sys.time(), "%b %d, %Y %H:%M")`

<html>

<p>

Copyright ©: `r format(Sys.time(), "%Y")` StatLab, BIO5 ALL RIGHTS RESERVED

</p>

<p>

Developer:

</p>

<p>

Lisa White, Statistician <br/>

</p>
