---
title: "HML ID Assignment"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    css: custom.css
    social: menu
    logo: PAN_logo3.png
    favicon: PAN_logo3.png
runtime: shiny
editor_options:
  chunk_output_type: console
---

```{=html}
<style type="text/css">

  .chart-title {  /* chart_title  */
    font-size: 22px;

</style>
```

```{r setup, include=FALSE}

library(tidyverse)
library(shiny)
library(flexdashboard)
# devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0")
# Need to use the above to collapse rows properly
library(kableExtra)
library(openxlsx)

# section to connect to Google Drive
library(googledrive)
# file with info for service account
drive_auth(path = "pan-mindcrowd-uploads-d9b7ecb93e53.json")
# Option to silence the messages coming from the Google Drive library
options(googledrive_quiet = TRUE)

# # Section to connect to Box Drive
# library(jsonlite)
# library(RCurl)
# 
# json_data <- fromJSON("keys.json")
# logininfo <- json_data$userpwd
# hmlfile <- "ftps://ftp.box.com/[UA%20BOX%20Health]%20MindCrowd%20Inbound/HML_ID_Assignment/deidentified_id_data.csv"

production <- TRUE

```

```{r load data}

# Downloads deidentified_id_data.csv and all_screening_data_processed.Rdata and overwrites existing files
# If not in production, will download files from local folder

if(production){
  with_drive_quiet(
    drive_download(as_id("https://drive.google.com/file/d/1NWUkcoIRuHBlw1h6_LWRlNpQSTcNa3fr"),
                   overwrite = TRUE)
  )
  load_data <- readRDS("generate_hml_id_dat.Rds")
  
  dat <- load_data$dat
  all_dat <- load_data$all_dat
  
  # Code to send data to Box
  # con <- textConnection(getURL(hmlfile, userpwd=logininfo, ftp.ssl=TRUE, 
  #                              ftp.use.epsv=FALSE, ftp.skip.pasv.ip=TRUE))
  # dat <- read.csv(con, header = T)
  
}else{
  with_drive_quiet(
    drive_download(as_id("https://drive.google.com/file/d/1UQVR0ri2KUlnMyl92pZSn5dnTL_XJzeN"),
                   overwrite = TRUE)
  )
  load_data <- readRDS("generate_hml_id_dat_test.Rds")
  
  dat <- load_data$dat
  all_dat <- load_data$all_dat
  
}

```

```{r save data}

save_data <- function(production, deidentified_id_dat, hml_id_dat, all_dat){
  
  if(production){
    # Saves the modified files to HML Data shared drive
    saveRDS(list(dat = deidentified_id_dat,
                 all_dat = all_dat),
            file = "generate_hml_id_dat.Rds")
    
    drive_put("generate_hml_id_dat.Rds", path=drive_find(pattern="HML Data", corpus="allDrives"))
  }else{
    
    saveRDS(list(dat = deidentified_id_dat,
                 all_dat = all_dat),
            file = "generate_hml_id_dat_test.Rds")
    
    drive_put("generate_hml_id_dat_test.Rds", path=drive_find(pattern="HML Data", corpus="allDrives"))
  }
  
  # Pop up status message and page reload
  shinyalert::shinyalert('Saved', callbackJS = "function() {location.reload()}")
}

```

```{r create ID server}

# Filter IDs by input area areaPick ------
id_choices <- reactive(
  filter(dat, area == input$areaPick, !is.na(participant_id))
)

# Filter data by selected ID idPick -------
picked_id_data <- reactive(
  filter(dat, participant_id == input$idPick & area == input$areaPick)
)

# Create new ID and add to dataset for confirmation -------
new_data <- reactive({
  req(input$newId)
  
  if(!is.na(dat$hml_id_undo[which(dat$participant_id == (input$idPick))])){
    new_hml_id <- dat$hml_id_undo[which(dat$participant_id == (input$idPick))]
  }else{
    existing_ids <- as.numeric(str_sub(c(dat$hml_id, dat$hml_id_undo), start = 4))
    
    existing_ids <- existing_ids[which(!is.na(existing_ids))]
    
    new_id <- max(existing_ids) + 1
    
    new_hml_id <- paste0("HML", str_pad(new_id, 4, pad = 0))
  }
  
  dat$hml_id[which(dat$participant_id == (input$idPick))] <- new_hml_id
  dat$hml_id_created_date[which(dat$participant_id == (input$idPick))] <- as.character(format(Sys.Date(), "%Y-%m-%d"))
  
  dat
})

# Save new ID data to Drive ------------

downloadNewData <- observe({
  if(isTruthy(input$saveId)){
    
    new_download <- new_data()
    
    # Update the all screening data so we don't overwrite any IDs
    all_dat <- all_dat %>%
      left_join(new_download %>% select(participant_id_parent = participant_id, hml_id, hml_id_created_date),
                by = "participant_id_parent") %>%
      mutate(hml_id = coalesce(hml_id.x, hml_id.y),
             hml_id_created_date = coalesce(hml_id_created_date.x, hml_id_created_date.y)) %>%
      select(-c(hml_id.x, hml_id.y, 
                hml_id_created_date.x, hml_id_created_date.y))
    
    # Save data
    save_data(production, 
              deidentified_id_dat = new_download, 
              hml_id_dat = filter(new_download, !is.na(hml_id)) %>% select(-hml_id_undo), 
              all_dat = all_dat)
  }
})

```

```{r undo ID server}

# Filter IDs by input area areaPick and display assigned IDs -------
id_choices_undo <- reactive(
  filter(dat, area == input$areaPick, !is.na(hml_id))
)

# Add undone ID and save to Drive -----------
downloadNewDataUndo <- observe({
  if(isTruthy(input$saveIdUndo)){
    new_dat <- dat
    
    new_dat$hml_id_undo[which(new_dat$hml_id == input$idPickUndo)] <- input$idPickUndo
    new_dat$hml_id[which(new_dat$hml_id == input$idPickUndo)] <- NA
    
    # Update the all screening data so we don't overwrite any IDs
    all_dat$hml_id[which(all_dat$hml_id == input$idPickUndo)] <- NA
    
    save_data(production,
              deidentified_id_dat = new_dat,
              hml_id_dat = filter(new_dat, !is.na(hml_id)) %>% select(-hml_id_undo),
              all_dat = all_dat)
  }
})

```

```{r manual ID upload server}

# Download uploaded data for confirmation and editing  ------------
id_data <- eventReactive(input$data_up, {
  req(input$data_up)
  
  id_data <- ifelse(tools::file_ext(input$data_up$datapath) == "csv",
                    read.csv(input$data_up$datapath, col.names = FALSE),
                    read.xlsx(input$data_up$datapath, colNames = FALSE))
})

# Add new HML IDs ------------
new_id_data <- reactive({
  id_data <- data.frame(id_data())
  
  # Detect variable name and remove row if present
  if(!str_detect(id_data[1,1], "[0:9]")) id_data <- as.data.frame(id_data[-1,])
  
  id_data <- rename(id_data, "id" = 1)
  
  # Check if ID already has HML
  
  check_data <- left_join(id_data[1], all_dat, by = c("id" = "alternative_id")) %>%
    # Add in area if already has HMl ID assigned from recruitment area
    left_join(select(dat, participant_id_parent = participant_id, area, hml_id_undo), by = "participant_id_parent")

  existing_ids <- as.numeric(str_sub(c(dat$hml_id, dat$hml_id_undo), start = 4))
  existing_ids <- existing_ids[which(!is.na(existing_ids))]
  
  new_ids <- check_data %>%
    # Assign any IDs that were previously undone
    mutate(hml_id = ifelse(!is.na(hml_id_undo), hml_id_undo, hml_id)) %>%
    select(-hml_id_undo) %>%
    select(participant_id_parent, hml_id, hml_id_created_date) %>%
    # Group any duplicated IDs
    distinct(participant_id_parent, .keep_all = T) %>%
    # Assign new HML IDs
    arrange(!is.na(hml_id)) %>%
    mutate(assigned = ifelse(!is.na(hml_id), "Already assigned HML ID", ""),
           hml_id_created_date = ifelse(is.na(hml_id),
                                        as.character(format(Sys.Date(), "%Y-%m-%d")),
                                        hml_id_created_date),
           hml_id = ifelse(is.na(hml_id),
                           paste0("HML", str_pad(max(existing_ids) + row_number(), 4, pad = 0)),
                           hml_id))
  
  # Add new HML IDs to submitted data list
  new_id_dat <- check_data %>%
    select(-starts_with("hml_id")) %>%
    mutate(area = ifelse(is.na(area), input$area_up, area)) %>%
    left_join(new_ids, by = "participant_id_parent")
  
  new_id_dat

})

# Submit new data ------------

downloadManualData <- observe({
  if(isTruthy(input$saveIdData)){
    new_id_dat <- new_id_data()
    
    down_id_dat <- dat %>% 
      # Remove any participants already in the deidentified_id_data
      filter(!participant_id %in% new_id_dat$participant_id_parent) %>%
      # Join new participants with HML IDs to deidentified_id_data
      rbind(new_id_dat %>%
              rename(participant_id = participant_id_parent,
                     memory_rank = task_group) %>%
              select(-c(id, assigned)) %>%
              mutate(hml_id_undo = NA))
    
    # Update the all screening data so we don't overwrite any IDs
    all_dat <- all_dat %>%
      left_join(new_id_dat %>% select(participant_id_parent, hml_id, hml_id_created_date),
                by = "participant_id_parent") %>%
      mutate(hml_id = coalesce(hml_id.x, hml_id.y),
             hml_id_created_date = coalesce(hml_id_created_date.x, hml_id_created_date.y)) %>%
      select(-c(ends_with(".x"), ends_with(".y")))
    
    save_data(production,
              deidentified_id_dat = down_id_dat,
              hml_id_dat = filter(down_id_dat, !is.na(hml_id)) %>% select(-hml_id_undo),
              all_dat = all_dat)
  }
})

```

<br>

{.sidebar}
===================

<br>

```{r select area}

# Select recruitment area
radioButtons("areaPick", label = "Please select the participant's recruitment area.",
            choices = c("Atlanta", "Baltimore", "Miami", "Tucson"))

```

# Generate New HML ID

## Row

#### 

<center>

```{r display id dropdown}

# Display IDs from selected area (areaPick)
renderUI(
  selectInput("idPick", label = "Select the participant's MindCrowd ID.",
              choices = c("",id_choices()$participant_id), selected = NULL)
)

```

```{r display participant info}

# Display selected participant's (idPick) demographics
renderUI(
  HTML(
    if(isTruthy(input$idPick)){
      kable(picked_id_data() %>% select(participant_id, area, age_group, sex),
            col.names = c("Mindcrowd Participant Parent ID", "Area", "Age Group", "Sex"),
            align = "c") %>%
        kable_styling(full_width = FALSE)
    }
  )
)

```

</center>

```{r check if participant has id}

# Gives feedback for whether participant already has an HML ID saved
renderText(
  HTML(
    if(isTruthy(input$idPick)){
      if(!is.na((picked_id_data()$hml_id))){ 
        # If participant already has an HMl ID
        paste0("This participant was assigned HML ID ", picked_id_data()$hml_id," on ", as.Date(picked_id_data()$hml_id_created_date) %>% format("%b %d, %Y"), ".")
      }else{ 
        # If person doesn't have an ID yet
        "This participant does not have an HML ID yet."
      }
    }
  )
)

```

```{r eligibility confirmation}

# Get user input for whether participant is eligible for study (eligiblePick) and doesn't have an HML ID
renderUI(
  # Display if user selects an ID
  if(isTruthy(input$idPick)){ 
    # If participant does not have an HML ID
    if(is.na((picked_id_data()$hml_id))){
      radioButtons("eligiblePick", label = "Is this person eligible for the study?",
                   choices = c("Yes", "No"), selected = "No")
    }
  }
)

```

```{r creating HML ID new}

# Display button if participant is eligible for study
renderUI(
    if(isTruthy(input$idPick) & isTruthy(input$eligiblePick)){
      if(input$eligiblePick == "Yes" & is.na((picked_id_data()$hml_id))){
        actionButton("newId", "Create New HML ID", icon = icon("plus"))
      }
    }
)

# Show data with new HML ID for confirmation
renderUI({
  # If there is an eligiblePick object created
  if(isTruthy(input$idPick) & isTruthy(input$eligiblePick)){ 
    # Only show button if person does not already have an HML ID
    if(input$eligiblePick == "Yes" & is.na((picked_id_data()$hml_id))){
      HTML(
        new_data()[which(dat$participant_id == input$idPick),] %>%
          remove_rownames() %>%
          select(c(participant_id, area, age_group, sex, hml_id, hml_id_created_date)) %>%
          kable(col.names = c("Mindcrowd Participant Parent ID", "Area", "Age Group", "Sex",
                              "HML ID", "HML ID Created Date"),
                align = "c") %>%
          kable_styling(full_width = FALSE)
      )
    }
  }
})

```

```{r save new id}

renderUI(
  if(isTruthy(input$idPick) & isTruthy(input$newId)){
    if(is.na((picked_id_data()$hml_id))){
      actionButton("saveId", "Save New HML ID", icon = icon("download"))
    }
  }
)

```

---

# Manual ID Upload

## Row

Manual ID Upload:

If you cannot find the participant ID in the dropdown menu, or the participant is outside of the recruitment area, please select a recruitment area and upload a csv file with the participants' participant_id_parent, participant_id, or P2 MCID.

If the submitted participant already has an HML ID, their ID and the date their ID was assigned will be displayed along with the newly created IDs for new participants.

<center>

```{r area select}

renderUI({
  selectInput("area_up", label = "Select recruitment area.",
              choices = c("", "Atlanta", "Baltimore", "Miami", "Tucson"), selected = NULL)
})

```

```{r data upload}

fileInput("data_up", 
          label = "Upload list of IDs.",
          accept = c(".csv", ".xlsx")
)

```

```{r display list}

# Display ID dataset
renderUI(
  HTML(
    if(isTruthy(input$area_up) & isTruthy(input$data_up)){
      new_id_data() %>% 
        select(id, participant_id_parent, area, age_group, sex, hml_id, hml_id_created_date, assigned) %>%
        kable(align = "c",
              col.names = c("Submitted ID", "Participant ID Parent", "Area", "Age Group", "Sex", "HML ID", "HML ID Created Date", " ")) %>% 
        kable_styling(full_width = FALSE)
    }
  )
)

```

```{r submit data}

renderUI(
    if(isTruthy(input$area_up) & isTruthy(input$data_up)){
        actionButton("saveIdData", "Confirm and Submit", icon = icon("download"))
    }
)

```

</center>

---

# Undo HML ID

## Row

Undo HML ID Assignment:

If you assigned a new HML ID by mistake, please select the participant's HML ID from the dropdown menu and press the "Undo New HML ID" button below.

<center>

```{r undo hml dropdown}

# Display IDs from selected area (areaPick) and has an assigned ID
renderUI({
  selectInput("idPickUndo", label = "Select the participant's MindCrowd ID.",
              choices = c("",id_choices_undo()$hml_id), selected = NULL)
})

```

</center>

```{r undo hml button}

renderUI(
    if(isTruthy(input$idPickUndo)){
        actionButton("saveIdUndo", "Undo New HML ID", icon = icon("delete-left"))
    }
)

```

---

# Help

## Row

```{r}
# 08-Feb-24: Added Help tab
tags$iframe(style = "height:850px; width:100%; scrolling=yes",
            src = "HML ID generation application_Help Document Version2_2023-08-23.pdf")

```

