---
title: "Participant Tracking"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    css: custom.css
    social: menu
    logo: PAN_logo3.png
    favicon: PAN_logo3.png
runtime: shiny
editor_options: 
  chunk_output_type: console
---

```{=html}
<style type="text/css">

  .chart-title {  /* chart_title  */
    font-size: 22px;

</style>
```
<!-- Server -->

```{r setup, include=FALSE}

library(tidyverse)
library(shiny)
library(flexdashboard)
library(plotly)
# devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0")
# Need to use the above to collapse rows properly
library(kableExtra)

# section to connect to Google Drive
library(googledrive)
# file with info for service account 
googledrive::drive_auth(path = "pan-mindcrowd-uploads-d9b7ecb93e53.json")

# Option to silence the messages coming from the Google Drive library
options(googledrive_quiet = TRUE)

```

```{r load data}

with_drive_quiet(
  drive_download(as_id("https://drive.google.com/file/d/19n2UvCBF375vVU1bGhVWht7rqZd1uNl0"), 
                 overwrite = TRUE)
)
load("hml_redcap_data.Rdata")

all_mindcrowd_data <- mutate(all_mindcrowd_data,
                             race_group = ifelse(race_group == "Hispanic", "Hispanic/Latino", race_group))

prescreen_data <- screening_data %>%
  rename(paired_associates = task_group) %>%
  mutate(# Create quarter time variable:
    day_time = as.Date(created_at, format = "%Y-%m-%d"),
    quarter_time = paste0(format(day_time, "%Y"), " ", quarters(day_time)),
    race_group = ifelse(race_group == "Hispanic", "Hispanic/Latino", race_group))

```

```{r descriptive functions}

# vars = variables to stratify counts by area and overall
table_function <- function(data, vars = NULL){
  
  # Get total participants by area
  site_counts <- count(data, area) %>% arrange(area)
  
  if(!is.null(vars)){
    
    totals <- c("Total", rep("", length(vars)-1), site_counts$n, sum(site_counts$n, na.rm = TRUE))
    
    table_data <- data %>%
      select(area, all_of(vars)) %>%
      # Replace any missing factor levels with "Missing"
      mutate(across(everything(), ~ifelse(. == "", "Missing", as.character(.)))) %>%
      # Counts by area and selected variables
      group_by_all() %>% summarise(n = n()) %>% ungroup() %>%
      # # Pivot so each column is a site
      pivot_wider(names_from = area,
                  values_from = n) %>%
      # Add overall counts by variable combination
      mutate(across(everything(), ~ifelse(is.na(.), 0, .))) %>%
      mutate(Total = select(., all_of(site_counts$area)) %>% rowSums()) %>%
      select(all_of(vars), all_of(site_counts$area), Total) %>%
      arrange(across(vars)) %>%
      # Add overall counts by site
      rbind(totals)
    
  }else{
    
    table_data <- data %>%
      select(area) %>%
      # Counts by area
      group_by_all() %>% summarise(n = n()) %>% ungroup() %>%
      # Pivot so each column is a site
      pivot_wider(names_from = area,
                  values_from = n) %>%
      # # Add overall counts by variable combination
      mutate(Total = select(., site_counts$area) %>% rowSums()) %>%
      select(all_of(site_counts$area), Total)
    
  }
  return(table_data)
}

# vars = variables to stratify counts by area and overall
# denom = dataset to add denominators under "data" counts in table
kable_function <- function(data, vars = NULL, denom = NULL){
  # Create table with denominators
  if(!is.null(denom)){
    numer <- table_function(data, vars) %>% 
      pivot_longer(cols = -vars,
                   values_to = "numer")
    denom <- table_function(denom, vars) %>% 
      pivot_longer(cols = -vars,
                   values_to = "denom")
    
    new_table <- full_join(numer, denom, by = c(vars, "name")) %>%
      mutate(numer = ifelse(is.na(numer), 0, numer),
             frac = paste0(numer, "/", denom)) %>%
      pivot_wider(id_cols = vars,
                  names_from = name,
                  values_from = frac) %>%
      arrange(across(vars)) %>%
      select(all_of(vars), "Atlanta", Baltimore, Miami, Tucson, Total) 
    
  }else{
    new_table <- table_function(data, vars)
  }
  
  # Create formatted table
  if(!is.null(vars)){
    kable_data <- new_table %>% 
      rename_all(~str_to_title(str_replace(., "_", " "))) %>%
      kable() %>%
      kable_styling(full_width = F) %>%
      collapse_rows(columns = 1:(length(vars)-1), valign = "top")
  }else{
    kable_data <- new_table %>%
      kable() %>%
      kable_styling(full_width = F)
  }
  return(kable_data)
}

# time = time increments to group counts and plot along x-axis
plot_function <- function(data, time){
  plot <- data %>%
    filter(!is.na(day_time)) %>%
    mutate(
      x_label = str_replace({{time}}, " ", "\n")
      ,x_label = fct_reorder(x_label, day_time)
      ) %>%
    group_by(x_label) %>% 
    count() %>% ungroup() %>%
    arrange(x_label) %>%
    mutate(running_total = cumsum(n)) %>%
    ggplot(aes(x = x_label, y = running_total, group = 1)) +
    geom_line(linewidth = 1, color = "#224A7B") +
    labs(x = "Time", y = "Cumulative Total") +
    theme_bw() +
    theme(panel.background = element_rect(fill='transparent'),
          plot.background = element_rect(fill='transparent', color=NA))
  
  ggplotly(plot)
}


```

<!-- UI -->

Mindcrowd Population
=====================================  

Inputs {.sidebar}
-------------------------------------

#### Last MindCrowd test taken: `r format(as.Date(max(all_mindcrowd_data$day_time), "%y%m%d"), "%b-%d-%Y")`

```{r mindcrowd inputs}
checkboxGroupInput("mindcrowd_vars", h4("Stratification Factors:"),
                   c("Age Group" = "age_group", 
                     "Sex" = "sex", 
                     "Race Group" = "race_group", 
                     "Paired Associates Test" = "paired_associates"),
                   selected = c("age_group", "sex"))
```

Row
-------------------------------------

All MindCrowd paired associates test participants:

<center>

```{r mindcrowd graph}
renderPlotly(plot_function(all_mindcrowd_data, year_time))
```

</center>
---

```{r mindcrowd table}
output$mindcrowd_table <- renderText(kable_function(all_mindcrowd_data, input$mindcrowd_vars))
htmlOutput("mindcrowd_table")
```

Mindcrowd Prescreen Eligible
=====================================  

Inputs {.sidebar}
-------------------------------------

#### Last MindCrowd test taken within MindCrowd prescreen eligible: `r format(as.Date(max(prescreen_data$day_time), "%y%m%d"), "%b-%d-%Y")`

```{r prescreen inputs}
checkboxGroupInput("prescreen_vars", h4("Stratification Factors:"),
                   c("Age Group" = "age_group", 
                     "Sex" = "sex", 
                     "Race Group" = "race_group", 
                     "Paired Associates Test" = "paired_associates"),
                   selected = c("age_group", "sex"))
```

Row
-------------------------------------

Potential participants within 60 miles of a recruitment site and fit the study requirements:

<center>

```{r prescreen graph}
renderPlotly(plot_function(prescreen_data, quarter_time))
```

</center>
---

```{r prescreen table}
output$prescreen_table <- renderText(kable_function(prescreen_data, input$prescreen_vars))
htmlOutput("prescreen_table")
```

HML Recruited
=====================================  

Inputs {.sidebar}
-------------------------------------

#### Data were last pulled from REDCap on: `r format(as.Date(max(hml_data$update_date), "%y%m%d"), "%b-%d-%Y")`

```{r recruit inputs}

checkboxGroupInput("recruit_vars", h4("Stratification Factors:"),
                   c("Age Group" = "age_group", 
                     "Sex" = "sex", 
                     "Race Group" = "race_group", 
                     "Paired Associates Test" = "paired_associates"),
                   selected = c("age_group", "sex"))

checkboxInput("compare_prescreen", h5("Table by Pre-Screen Population"), value = FALSE)

```

Row
-------------------------------------

Participants assigned an HML ID (and are in REDCap):

<center>

```{r recruit graph}
renderPlotly(plot_function(hml_data, quarter_time))
```

</center>

---

```{r recruit table}

conditionalPanel(condition = "!input.compare_prescreen", htmlOutput("recruit_table"))
conditionalPanel(condition = "input.compare_prescreen", 
                 textOutput("compare_recruit_text"), 
                 textOutput("compare_note_text"),
                 htmlOutput("recruit_prescreen_table")
                 )

output$compare_recruit_text <- renderText(print("HML Recruited / Prescreen Eligible"))
output$compare_note_text <- renderText(print("Note: NA in the denominator means the participants were recruited outside of the prescreen eligible list."))

output$recruit_table <- renderText(kable_function(hml_data, input$recruit_vars))

output$recruit_prescreen_table <- renderText(kable_function(hml_data, input$recruit_vars, 
                                                            denom = prescreen_data))

```

HML Consented
=====================================  

Inputs {.sidebar}
-------------------------------------

#### Data were last pulled from REDCap on: `r format(as.Date(max(hml_data$update_date), "%y%m%d"), "%b-%d-%Y")`

```{r consent inputs}
checkboxGroupInput("consented_vars", h4("Stratification Factors:"),
                   c("Age Group" = "age_group", 
                     "Sex" = "sex", 
                     "Race Group" = "race_group", 
                     "Paired Associates Test" = "paired_associates"),
                   selected = c("age_group", "sex"))

radioButtons("nonmissing", h5("Compare Counts"), 
            choices = c("Only consented participants" = "consent",
                        "Compare to consented to recruited participants" = "compare",
                        "Compare to non-missing counts" = "missing"),
            selected = "consent")

```

Row
-------------------------------------

Participants with a REDCap main_consent_date:

<center>

```{r consent graph}
conditionalPanel(condition = "input.nonmissing == 'consent' | input.nonmissing == 'compare'", plotlyOutput("consented_plot"))

conditionalPanel(condition = "input.nonmissing == 'missing'", plotlyOutput("nonmissing_plot"))

output$consented_plot <- renderPlotly(plot_function(consented, quarter_time))
output$nonmissing_plot <- renderPlotly(plot_function(consented %>%
                                          filter(Overall == "Complete Neuropsych and Biometrics"), 
                                        quarter_time))
```

</center>
---

```{r consent table}
conditionalPanel(condition = "input.nonmissing == 'consent'", htmlOutput("consented_table"))

conditionalPanel(condition = "input.nonmissing == 'missing'", textOutput("nonmissing_text"), 
                 htmlOutput("nonmissing_table"))

conditionalPanel(condition = "input.nonmissing == 'compare'", textOutput("compare_text"),
                 htmlOutput("compare_table"))

output$consented_table <- renderText(kable_function(consented, input$consented_vars))
output$nonmissing_table <- renderText(kable_function(consented %>%
                                                       filter(Overall == "Complete Neuropsych and Biometrics"), 
                                                     input$consented_vars, 
                                                     denom = consented))
output$compare_table <- renderText(kable_function(consented, input$consented_vars, denom = hml_data))

output$nonmissing_text <- renderText(print("HML Non-Missing Cognitive or Biometrics Data / HML Consented"))
output$compare_text <- renderText(print("HML Consented / HML Recruited"))
```


